### 2024-09-14 Response/Response.tex

where $\mathbbm{1} (z \in \mathbb{Z})$ is the indicator function. In particular, the total processing capacity that EN $j$ allocates to MD $i$ from the time slot $\hat{l}_{i,j}^{\text{E}}(t)$ to the time slot $l_{i,j}^{\text{E}}(t)$ should exceed the size of task $z_{i,j}^{\text{E}}(t)$. Conversely, the total allocated processing capacity from the time slot $l_{i,j}^{\text{E}}(t)$ to the time slot $l_{i,j}^{\text{E}}(t)-1$ should be less than the task's size.

Additionally, we define $D_{i,j}^{\text{E}}(t)$ to represent the quantity of processing time slots allocated to task $z_{i,j}^{\text{E}}(t)$ when executed at EN $j$. This value is given by:
\begin{alignat}{1}
	D_{i,j}^{\text{E}}(t) = { \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over f_j^{\text{E}} \tau /  b_j(t)}.
	\label{14}  
\end{alignat}
We also define $E_{i,j}^{\text{E}}(t)$ as the energy consumption of processing at EN $j$ in time slot $t$ by MD $i$. This can be calculated as:
\begin{alignat}{1}
	E_{i,j}^{\text{E}}(t) = {D_{i,j}^{\text{E}}(t)  p_j^{\text{E}} \tau \over b_j(t)},  % = { \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over  f_j^{\text{E}}}p_j^{\text{E}} ,
	\label{15}  
\end{alignat}
where $p_j^{\text{E}}$ is a constant value which denotes the energy consumption of the EN $j$'s processor when operating at full capacity.

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i,j}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
\begin{alignat}{1}
	E_i^{\text{I}}(t) = D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.
\begin{alignat}{1}
	E_i^{\text{O}}(t) = E_i^{\text{T}}(t) + \sum_{\mathcal{J}} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t).
	\label{17}
\end{alignat}

\section{Task Offloading problem Formulation}
\label{section:III}

Based on the introduced system model, we present the computation task offloading problem in this section. Our primary goal is to enhance each MD's QoE individually by taking the dynamic demands of MDs into account. To achieve this, we approach the optimization problem as an MDP, aiming to maximize the MD's QoE by striking a balance among key QoE factors, including task completion, task delay, and energy consumption. To prioritize QoE factors, we utilize the MD's battery level, which plays a crucial role in decision-making. Specifically, when an MD observes its state (e.g. task size, queue details, and battery level) and encounters a newly arrived task, it selects an appropriate action for that task. The selected action, based on the observed state, will result in enhanced QoE. Each MD strives to maximize its long-term QoE by optimizing the policy mapping from states to actions. In what follows, we first present the state space, action space, and QoE function, respectively. We then formulate the QoE maximization problem for each MD.

\subsection{State Space}
A state in our MDP represents a conceptual space that comprehensively describes the state of an MD facing the environment. We represent the MD $i$'s state in time slot $t$ as vector $\boldsymbol{s}_i(t)$ that includes the newly arrived task size, the queues information, the MD's battery level, and the workload history at the ENs. The MD observers this vector at the beginning of each time slot. The vector $\boldsymbol{s}_i(t)$ is defined as follows:
\begin{alignat}{1}
	\boldsymbol{s}_i(t) = \Big(\lambda_i(t), \delta_i^{\text{C}}(t), \delta_i^{\text{T}}(t), \boldsymbol{\eta}_i^{\text{E}}\hspace{-0.4mm}(\hspace{-0.4mm}t\hspace{-0.4mm}-\hspace{-0.4mm}1\hspace{-0.5mm}),\phi_i(t), \mathcal{H}(t) \Big),
	\label{18}
\end{alignat}
where vector $\boldsymbol{\eta}_i^{\text{E}}(t-1) = (\eta_{i,j}^{\text{E}}(t-1))_{j \in \mathcal{J}}$ represents the queues length of MD $i$ in ENs at the previous time slot and is computed by the MD according to \eqref{10}. Let $\phi_i(t)$ denote the battery level of MD $i$ in time slot $t$. Considering the power modes of a real mobile device, $\phi_i(t)$ is derived from the discrete set $\Phi=\{\phi_1,\phi_2,\phi_3\}$, corresponding to ultra power-saving, power-saving, and performance modes, respectively.

In addition, to predict future EN workloads, we define the matrix $\mathcal{H}(t)$ as historical data, indicating the number of active queues for all ENs. This data is recorded over $T^{\text{s}}$ time slots, ranging from $t\hspace{-0.4mm}-\hspace{-0.4mm}T^{\text{s}}$ to $t\hspace{-0.4mm}-\hspace{-0.4mm}1$, in $T^{\text{s}}\hspace{-0.4mm}\times \hspace{-0.4mm} J$ matrix. For EN $j$ workload history at $i^{th}$ time slot from $T^{\text{s}}-t$, we define $h_{i,j}(t)$ as:
\begin{alignat}{1}
	h_{i,j}(t) = b_j(t - T^{\text{s}} + i - 1).
	\label{19}
\end{alignat}
%where $b_j(t - T^{\text{s}} + i - 1)$ is the number of active queues of EN $j$ in time slot $t - T^{\text{s}} + i - 1$. 
EN $j \in \mathcal{J}$ broadcasts $b_j(t)$ at the end of each time slot. %Given $b_j(t) \leq I$, can be represented using only a few bits, the broadcast incurs minimal signaling overhead.

We define vector $\mathcal{S}$ as the discrete and finite state space for each MD. The size of the set $\mathcal{S}$ is given by $\Lambda \times T^2 \times \mathcal{U} \times 3 \times I^{T^{\text{s}} \times J}$, where $\mathcal{U}$ is the set of available queue length values at an EN over $T$ time slots.

%A MD $i \in \mathcal{I}$ can obtain state information $\lambda_i(t)$, $\delta_i^{\text{C}}(t)$, $\delta_i^{\text{T}}(t)$, and $\phi_i(t)$ through local observation at the beginning of time slot $t$.

%For state information  $\boldsymbol{\eta}_i^{\text{E}}(t-1)$, MD $i$ can compute this vector according to the number of transmitted bits to each EN in each time slot and the number of bits of MD $i$ processed or being dropped by each EN in each time slot according to \eqref{10}.

%For matrix $\mathcal{H}(t)$, we assume that each EN will broadcast its number of active queues at the end of each time slot. Since the number of active queues is always a small number, which can be represented by several bits, the broadcasting will only incur a small signaling overhead.

\subsection{Action Space}
The action space represents the agent's behavior and the decisions. In this context, we define $\boldsymbol{a}_i(t)$ to denote the action taken by MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. These actions involve two decisions, (a) Offloading decision to determine whether or not to offload the task, and (b) Offloading target to determine the EN to send the offloaded tasks. Thus, the action of MD $i$ in time slot $t$ can be concisely expressed as the following action tuple: \vspace{-1.5mm}
\begin{alignat}{1}
	\boldsymbol{a}_i(t) = (x_i(t), \boldsymbol{y}_i(t)),
	\label{20}
\end{alignat}
where vector $\boldsymbol{y}_i(t)=(y_{i,j}(t))_{j \in \mathcal{J}}$ represents the selected EN for offloading this task. In Section~\ref{section:1}, we will discuss about the size of this action space.

%Hence, the decision space of each MD is thus equal to $\mathcal{A} = \{0,1\}^{1+N}$, with $j$ representing the number of available ENs.

\subsection{QoE Function}
The QoE function evaluates the influence of agent's actions by taking several key performance factors into account. Given the selected action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$, we represent $\mathcal{D}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$ as the delay of task $z_i(t),$ which indicates the number of time slots from time slot $t$ to the time slot in which task $z_i(t)$ is processed. It is calculated by:

$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +$
\begin{alignat}{1}
	\;\;\;\; x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t')=z_i(t)\big) l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ when task $z_i(t)$ is dropped. Correspondingly, we denote the energy consumption of task $z_i(t)$ when taking action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$ as $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, which is: \vspace{1.7mm}

$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+$
\begin{alignat}{1}
	\hspace{1.8cm} x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}
Given the delay and energy consumtion of task $z_i(t)$, we also define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$. \vspace{1.7mm}

$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
	\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
	\label{23}  
\end{alignat}
where $\phi_i(t)$ represents the MD $i$'s battery level. When the MD is operating in performance mode, the primary focus is on minimizing task delays, thus the delay contributes more to the cost. On the other hand, when the MD switches to ultra power-saving mode, the main attention is directed toward reducing power consumption.

Finally, we define $\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ as the QoE associated with task $z_i(t)$ given the selected action $\boldsymbol{a}_i(t)$ and the observed state $\boldsymbol{s}_i(t)$. The QoE function is defined as follows:\vspace{1.7mm}

$\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
	\hspace*{8mm}
	\begin{cases} 
		\mathcal{R} - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) & \hspace*{-2mm} \text{if task $z_i(t)$ is processed,} \\
		- \hspace*{0.8mm} \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) &	\hspace*{-2mm} \text{if task $z_i(t)$ is dropped,}
	\end{cases}
	\label{26}  
\end{alignat}
where $\mathcal{R} > 0$ represents a constant reward for task completion. If $z_i(t) = 0$, then $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t)) = 0$. Throughout the rest of this paper, we adopt the shortened notation $\boldsymbol{q}_i(t)$ to represent $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$.
%When $\phi_i(t)$ is closer to 1, the cost function prioritizes reducing delay and drop, which could be advantageous in situations where tasks need to be completed quickly, and responsiveness is crucial. Conversely, when $\phi_i(t)$ is closer to 0, the cost function prioritizes reducing energy consumption, which is beneficial when the MD's battery level is low, and conserving power is necessary to prolong operation.

\subsection{Problem Formulation}
We define the task offloading policy for MD $i \in \mathcal{I}$ as a mapping from its state to its corresponding action, denoted by i.e., $\pi_i : \mathcal{S} \rightarrow \mathcal{A}$. Especially, MD $i$ determines an action $\boldsymbol{a}_i(t) \in \mathcal{A}$, according to policy $\pi_i$ given the observed environment state $\boldsymbol{s}_i(t) \in \mathcal{S}$. The MD aims to find its optimal policy $\pi_i^*$ which maximizes the long-term QoE,
\begin{alignat}{1}
	\pi_i^* = \text{arg}\,\,  \max\limits_{\pi_i}  \mathbbm{E} \Bigg[ \sum\limits_{t \in \mathcal{T}}  \gamma^{t-1}\boldsymbol{q}_i(t) \Bigg| \pi_i \Bigg],
	\label{24}  
\end{alignat}
where $\gamma \in (0,1]$ is a discount factor and determines the balance between instant QoE and long-term QoE. As $\gamma$ approaches 0, the MD prioritizes QoE within the current time slot exclusively. Conversely, as $\gamma$ approaches 1, the MD increasingly factors in the cumulative long-term QoE. The expectation $\mathbb{E}[\cdot]$ is taken into consideration of the time-varying system environments. Solving the optimization problem in \eqref{24} is particularly challenging due to the dynamic nature of the network. To address this challenge, we introduce a DRL- based offloading algorithm to learn the mapping between each state-action pair and their long-term QoE.
\section{DRL-Based Offloading Algorithm} \label{section:IV}
We now present QECO algorithm so as to address the distributed offloading decision-making of MDs. The aim is to empower MDs to identify the most efficient action that maximizes their long-term QoE. In the following, we introduce a neural network that characterizes the MD's state-action Q-values mapping, followed by a description of the information exchange between the MDs and ENs.

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{Fig/DQN}
	\captionsetup{name=Fig.}

	\caption{The neural network of MD $i \in \mathcal{I}$, which characterize the Q-value of each action $\boldsymbol{a} \in \mathcal{A}$ under state $\boldsymbol{s}_i(t) \in \mathcal{S}$.}
	\vspace*{-4.5mm}
	\label{DQN}
\end{figure}

\subsection{DQN-based Approach}
We utilize the DQN technique to find the mapping between each state-action pair to Q-values in the formulated MDP. As shown in Fig.~\ref{DQN}, each MD $i \in \mathcal{I}$ is equipped with a neural network comprising six layers. These layers include an input layer, an LSTM layer, two dense layers, an advantage-value (A\&V) layer, and an output layer. The parameter vector $\theta_i$ of MD $i$'s neural network is defined to maintain the connection weights and neuron biases across all layers. For MD $i \in \mathcal{I}$, we utilize the state information as the input of neural network. The state information $\lambda_i(t)$, $\delta_i^{\text{C}}(t)$, $\delta_i^{\text{T}}(t)$, $\phi_i(t)$, and $\boldsymbol{\eta}_i^{\text{E}}(t-1)$ are directly passed to the dense layer, while the state information $\mathcal{H}(t)$ is first supplied to the LSTM layer and then the resulting output is sent to the dense layer. The role and responsibilities of each layer are detailed as follows.

\subsubsection{Predicting Workloads at ENs}
In order to capture the dynamic behavior of workloads at the ENs, we employ the LSTM network \cite{hochreiter1997long}. This network maintains a memory state $\mathcal{H}(t)$ that evolves over time, enabling the neural network to predict future workloads at the ENs based on historical data. By taking the matrix $\mathcal{H}(t)$ as an input, the LSTM network learns the patterns of workload dynamics. The architecture of the LSTM consists of $T^{\text{s}}$ units, each equipped with a set of hidden neurons, and it processes individual rows of the matrix $\mathcal{H}(t)$ sequentially. Through this interconnected design, MD tracks the variations in sequences from $\boldsymbol{h}_1(t)$ to $\boldsymbol{h}_{T^{\text{s}}}(t)$, where vector $\boldsymbol{h}_i(t) = (h_{i,j}(t))_{j \in \mathcal{J}}$, thereby revealing workload fluctuations at the ENs across different time slots. The final LSTM unit produces an output that encapsulates the anticipated workload dynamics, and is then connected to the subsequent layer neurons for further learning.

%\subsubsection{workload Prediction}
%To learning the dynamics of the workloads at the ENs, we use the LSTM network [26], [27], which can keep track of the state $\mathcal{H}(t)$ over time. It can provide the neural network the ability of estimating the workloads at the ENs in the future using the history. The LSTM network takes the matrix $\mathcal{H}(t)$ as input so as to learn the workload dynamics. coresponding the matrix $\mathcal{H}(t)$,  The LSTM network contains $T^{\text{s}}$ LSTM units, each of which contains a set of hidden neurons and takes one row of the matrix $\mathcal{H}(t)$ as input. These LSTM units are connected in sequence so as to keep track of the variations of the sequences from $\{\mathcal{H}(t)\}_1$ to $\{\mathcal{H}(t)\}_{T^{\text{s}}}$, which can reveal the variations of the workloads at the ENs among time slots. The LSTM network will output the information that indicates the dynamics of the workloads in the future in the last LSTM unit, where the output will be connected to the neurons in the next layer for further learning.
%
%---------------------

### 2024-09-14 Response/Response.tex

%This layer is responsible for learning the dynamics of the workloads at the ENs. This is achieved by including an LSTM network [26], [27]. We use the LSTM network because it can keep track of the state $\textbf{H}(t)$ over time. It can provide the neural network the ability of estimating the workloads at the ENs in the future using the history. 
%
%Specifically, the LSTM network takes the matrix $\textbf{H}(t)$ as input so as to learn the workload dynamics. Fig. 3 shows the structure of an LSTM network. The LSTM network contains Tstep LSTM units, each of which contains a set of hidden neurons. Each LSTM unit takes one row of the matrix $\textbf{H}(t)$ as input, we let $\{\textbf{H}(t)\}_1$  denote the $i^{th}$ row of matrix $\textbf{H}(t)$ in Fig. 3. These LSTM units are connected in sequence so as to keep track of the variations of the sequences from $\{\textbf{H}(t)\}_1$ to $\{\textbf{H}(t)\}_{T^{step}}$, which can reveal the variations of the workloads at the ENs among time slots. The LSTM network will output the information that indicates the dynamics of the workloads in the future in the last LSTM unit, where the output will be connected to the neurons in the next layer for further learning.

\subsubsection{State-Action Q-Value Mapping}
The pair of dual dense layers plays a crucial role in learning the mapping of Q-values from the current state and the learned load dynamics to the corresponding actions. The dense layers consist of a cluster of neurons that employ rectified linear units (ReLUs) as their activation functions. In the initial dense layer, connections are established from the neurons in the input layer and the LSTM layer to each neuron in the dense layer. The resulting output of a neuron in the dense layer is connected to each neuron in the subsequent dense layer. In the second layer, the outputs from each neuron establish connections with all neurons in the A\&V layers.

\subsubsection{Dueling-DQN Approach for Q-Value Estimation}
In the neural network architecture, the A\&V layer and the output layer incorporate the principles of the dueling-DQN \cite{wang2016dueling} to compute action Q-values. The fundamental concept of dueling-DQN involves two separate learning components: one for action-advantage values and another for state-value. This approach enhances Q-value estimation by separately evaluating the long-term QoE attributed to states and actions.

The A\&V layer consists of two distinct dense networks referred to as network A and network V. Network A's role is to learn the action-advantage value for each action, while network V focuses on learning the state-value. For an MD $i \in \mathcal{I}$, we define $V_i(\boldsymbol{s}_i(t); \theta_i)$ and $A_i(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta_i)$ to denote the state-value and the action-advantage value of action $\boldsymbol{a} \in \mathcal{A}$ under state $\boldsymbol{s}_i(t) \in \mathcal{S}$, respectively. The parameter $\theta_i$ is responsible for determining these values, and it can be adjusted when training the QECO algorithm.

For an MD $i \in \mathcal{I}$, the A\&V layer and the output layer collectively determine $Q_i(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta_i)$, representing the resulting Q-value under action $\boldsymbol{a} \in \mathcal{A}$ and state $\boldsymbol{s}_i(t) \in \mathcal{S}$, as follows: \vspace{1.7mm}

$Q_i(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta_i) = V_i(\boldsymbol{s}_i(t);\theta_i) +$
\begin{alignat}{1}
	\hspace{0.94cm} \Bigg( A_i(\boldsymbol{s}_i(t),\boldsymbol{a};\theta_i) - {1 \over |\mathcal{A}|} \sum\limits_{\boldsymbol{a}' \in \mathcal{A}}(A_i(\boldsymbol{s}_i(t),\boldsymbol{a}';\theta_i) \Bigg),
	\label{25}  
\end{alignat}
where $\theta_i$ establishes a functional relationship that maps Q-values to pairs of state-action.

%, which characterizes the long-term QoE under any observed state $\boldsymbol{s}_i(t) \in \mathcal{S}$ and action $\mathcal{A} \in \mathcal{A}$.

%\begin{algorithm} [tbp]
%	\caption{QECO Algorithm (Offloading Decision)}\label{alg:cap}
%	\begin{algorithmic}[1]
	%		\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
	%		\renewcommand{\algorithmicensure}{\textbf{Output:}}
	%		\Require state space $\mathcal{S}$, action space $\mathcal{A}$
	%		\Ensure MD $i \in \mathcal{I}$ experience 
	%		\For {episode 1 to $N^{\text{ep}}$}
	%		\State Initialize $\boldsymbol{s}_i(1)$
	%		\For {time slot $t \in \mathcal{T}$}
	%		\If{MD $i$ receives a new task $z_i(t)$}
	%		\State Send an \textit{UpdateRequest} to EN $j_i$;
	%		\State Receive network parameter vector $\theta_i^{\text{E}}$;
	%		\State Select action $\boldsymbol{a}_i(t)$ based on \eqref{26};
	%		\EndIf
	%		\State Observe a set of QoEs $\{\boldsymbol{q}_i(t'), t' \in \mathcal{F}_i^t\}$;
	%		\State Observe\textcolor{white}{i}the next\textcolor{white}{i}state $\textbf{\textit{s}}_i(t+1)$;\textcolor{white}{i}
	%		\For {each task $z_i(t')$ where $t' \in \mathcal{F}_i^t$} 
	%		\State Send \hspace{-1mm} $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ to EN $j_i$;
	%		\EndFor
	%		\EndFor
	%		\EndFor
	%	\end{algorithmic}
%\end{algorithm}

\subsection{QoE-Oriented DRL-Based Algorithm}
\label{section:1}

%Our proposed QoE-Driven DRL-Based Algorithm is designed to efficiently distribute computational loads for training neural networks on MDs while leveraging the support of ENs. The primary objective of this algorithm is to utilize the experience of each MD to train its neural network, allowing the MD to make informed decisions that maximize its long-term QoE. To achieve efficient training, each MD $i \in \mathcal{I}$ is paired with a dedicated EN $n_i \in \mathcal{J}$ that assists in the training process. The selection of EN $n_i$ is based on its maximum transmission capacity with MD $i$. We define the set $\mathcal{I}_j \subset \mathcal{I}$ as the group of MDs whose training is facilitated by EN $j \in \mathcal{J}$.

The QECO algorithm is meticulously designed to optimize the allocation of computational tasks between MDs and ENs. Since the training of neural networks imposes an extensive computational workload on MDs, we enable MDs to utilize ENs for training their neural networks, effectively reducing their computational workload. For each MD $i \in \mathcal{I}$, there is an associated EN, denoted as EN $j_i \in \mathcal{J}$, which assists in the training process. This EN possesses the highest transmission capacity among all ENs. We define $\mathcal{I}_j \subset \mathcal{I}$ as the set of MDs for which training is executed by EN $j \in \mathcal{J}$, i.e. $\mathcal{I}_j = \{i \in \mathcal{I} | j_i = j\}$. This approach is feasible due to the minimal information exchange and processing requirements for training compared to MD's tasks. The algorithms to be executed at MD $i \in \mathcal{I}$ and EN $j \in \mathcal{J}$ are given in Algorithms ~\ref{alg:cap} and ~\ref{alg:cap2}, respectively. The core concept involves training neural networks with MD experiences (i.e., state, action, QoE, next state) to map Q-values to each state-action pair. This mapping allows MD to identify the action in the observed state with the highest Q-value and maximize its long-term QoE.

In detail, EN $j \in \mathcal{J}$ maintains a replay buffer denotes as $\mathcal{M}_i$ with two neural networks for MD $i$: $\textit{Net}_i^{\text{E}}$, denoting the evaluation network, and $\textit{Net}_i^{\text{T}}$, denoting the target network, which have the same neural network architecture. However, they possess distinct parameter vectors $\theta^{\text{E}}_i$ and $\theta^{\text{T}}_i$, respectively. Their Q-values are represented by $Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$ and $Q_i^{\text{T}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{T}}_i)$ for MD $i \in \mathcal{I}_j$, respectively, associating the action $\boldsymbol{a} \in \mathcal{A}$ under the state $\boldsymbol{s}_i(t) \in \mathcal{S}$. The replay buffer records the observed experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ of MD $i$. Moreover, $\textit{Net}_i^{\text{E}}$ is responsible for action selection, while $\textit{Net}_i^{\text{T}}$ characterizes the target Q-values, which represent the estimated long-term QoE resulting from an action in the observed state. The target Q-value serves as the reference for updating the network parameter vector $\theta^{\text{E}}_i$. This update occurs through the minimization of disparities between the Q-values under $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$. In the following, we introduce the offloading decision algorithm of MD $i \in \mathcal{I}$ and the training process algorithm running in EN $j \in \mathcal{J}$.

% i.e., $\textbf{\textit{s}}_i(1) = \big(\lambda_i(1), \delta_i^{\text{C}}(1), \delta_i^{\text{T}}(1), \boldsymbol{\eta}_i^{\text{E}}(0),\phi_i(1), \mathcal{H}(1) \big)$, where we set $\boldsymbol{\eta}_i^{\text{E}}(0)=0$ for all $j \in \mathcal{J}$, and $ \mathcal{H}(1)$ is a zero matrix with size $T^s \times N$.

\subsubsection{Offloading Decision Algorithm at MD $i \in \mathcal{I}$}
We analyze a series of episodes, where $N^{\text{ep}}$ denotes the number of them. At the beginning of each episode, if MD $i \in \mathcal{I}$ receives a new task $z_i(t)$, it initializes the state $\mathcal{S}_i(1)$ and sends an $\textit{UpdateRequest}$ to EN $j_i$. After receiving the requested vector $\theta_i^{\text{E}}$ of $\textit{Net}_i^{\text{E}}$ from EN $j_i$, MD $i$ chooses the following action for task $z_i(t)$.
\begin{alignat}{1}
	\hspace*{-2mm}\boldsymbol{a}_i(t) \hspace*{-0.5mm} = \hspace*{-0.5mm}
	\begin{cases} 
		\text{arg $\max_{\boldsymbol{a}\in \mathcal{A}}Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$,} & \text{w.p. $1-\boldsymbol{\epsilon}$,} \\
		\text{pick a random action from $\mathcal{A}$,} & \text{w.p. $\boldsymbol{\epsilon}$,}
	\end{cases}
	\label{26}  
\end{alignat}
where w.p. stands for with probability, and $\boldsymbol{\epsilon}$ represents the random exploration probability. The value of $Q_i^{\text{E}}(\boldsymbol{s}_i(t), \boldsymbol{a}; \theta^{\text{E}}_i)$ indicates the Q-value under the parameter $\theta^{\text{E}}_i$ of the neural network $\textit{Net}_i^{\text{E}}$. Specifically, the MD with a probability of $1 - \boldsymbol{\epsilon}$ selects the action associated with the highest Q-value under $\textit{Net}_i^{\text{E}}$ in the observed state $\boldsymbol{s}_i(t)$.

In the next time slot $t+1$, MD $i$ observes the state $\mathcal{S}_i(t+1)$. However, due to the potential for tasks to extend across multiple time slots, QoE $\boldsymbol{q}_i(t)$ associated with task $z_i(t)$ may not be observable in time slot $t+1$. On the other hand, MD $i$ may observe a group of QoEs associated with some tasks $z_i(t')$ in time slots $t' \leq t$. For each MD $i$, we define the set $\mathcal{F}_i^t \subset \mathcal{T}$ to denote the time slots during which each arriving task $z_i(t')$ is either processed or dropped in time slot $t$, as given by: \vspace{2mm}

$\mathcal{F}_i^t =\bigg \{ t' \bigg|\; t' \leq t,\; \lambda_i(t')>0, \; (1 - x_i(t')) \; l_i^{\text{C}}(t') \; + $ \vspace{-3mm}
\begin{equation}
	\hspace{20mm} x_i(t')\sum\limits_{\mathcal{J}} \sum\limits_{n= t'}^{t}\mathbbm{1}(z_{i,j}^{\text{E}}(n)=z_i(t'))  \; l_{i,j}^{\text{E}}(n) = t \bigg\}.
	\label{27}  
	\nonumber
\end{equation}
Therefore, MD $i$ observes a set of QoEs $\{\boldsymbol{q}_i(t') \mid t' \in \mathcal{F}_i^t\}$ at the beginning of time slot $t+1$, where the set $\mathcal{F}_i^t$ for some $i \in \mathcal{I}$ can be empty. Subsequently, MD $i$ sends its experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ to EN $j_i$ for each task $z_i(t')$ in $t' \in \mathcal{F}_i^t$.

%\begin{algorithm}[tbp]
%	\caption{QECO Algorithm (Training Process)}\label{alg:cap2}
%	\begin{algorithmic}[1]
	%		\State Initialize replay buffer $\mathcal{M}_i$ for each MD $i \in \mathcal{I}_j$;
	%		\State Initialize $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ with random parameters $\theta_i^{\text{E}}$ and $\theta_i^{\text{T}}$ respectively, for each MD $i \in \mathcal{I}_j$;
	%		\State Set Count := 0
	%		\While{True} \Comment{\textit{infinite loop}}
	%		\If{receive an \textit{UpdateRequest} from MD $i \in \mathcal{I}_j$}
	%		\State Send  $\theta_i^{\text{E}}$ to MD $i \in \mathcal{I}$;
	%		\EndIf
	%		\If {an experience \hspace{-0.2mm} $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$ is received \\ \;\;\;\; from MD $i \in \mathcal{I}_j$}
	%		\State Store $(\boldsymbol{s}_i(t'), \boldsymbol{a}_i(t'), \boldsymbol{q}_i(t'), \boldsymbol{s}_i(t'\hspace{-1mm}+1))$ in $\mathcal{M}_i$;
	%		\State Get a collection of experiences  $\mathcal{I}$ from $\mathcal{M}_i$; 
	%		\For{each experience $i \in \mathcal{I}$} 
	%		\State Get experience $(\boldsymbol{s}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}n\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}n\hspace{-0.5mm}+1\hspace{-0.2mm}))$; 
	%		\State Generate $\hat{Q}_{i,n}^{\text{T}}$ according to   \eqref{28};
	%		\EndFor
	%		\State Set vector  $\hat{\mathbf{Q}}_i^{\text{T}} := (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$;
	%		\State Update $\theta_i^{\text{E}}$ to minimize $L(\theta_i^{\text{E}}$, $\hat{\mathbf{Q}}_i^{\text{T}})$ in   \eqref{30};
	%		\State Count := Count + 1;
	%		\If {mod(Count, \textit{ReplaceThreshold}) = 0}
	%		\State $\theta_i^{\text{T}}$ := $\theta_i^{\text{E}}$;
	%		\EndIf
	%		\EndIf
	%		\EndWhile
	%		
	%	\end{algorithmic}
%\end{algorithm}

\subsubsection{Training Process Algorithm at EN $j \in \mathcal{J}$}
Upon initializing the replay buffer $\mathcal{M}_i$ with the neural networks $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$ for each MD $i \in \mathcal{I}_j$, EN $j \in \mathcal{J}$ waits for messages from the MDs in the set $\mathcal{I}_j$. When EN $j$ receives an $\textit{UpdateRequest}$ signal from an MD $i \in \mathcal{I}_j$, it responds by transmitting the updated parameter vector $\theta^{\text{E}}_i$, obtained from $\textit{Net}_i^{\text{E}}$, back to MD $i$. On the other side, if EN $j$ receives an experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ from MD $i \in \mathcal{I}_j$, the EN stores this experience in the replay buffer $\mathcal{M}_i$ associated with that MD. %The replay buffer operates at maximum capacity and FIFO principle.
